---
title: 'Model_Test  Assignment: 6 [Group: PRJ 4] '
output:
  word_document: default
  pdf_document: default
date: "2023-07-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

   

## Installing and Loading the required packages
```{r}
# install.packages("tidyverse")
# install.packages("caret")
# install.packages("data.table")
# install.packages("tidyr")
# install.packages("stringr")
# install.packages("forcats")
# install.packages("ggplot2")
# install.packages("kableExtra")
#install.packages("kernlab")
#install.packages("gam")
#install.packages("kknn")
#install.packages("igraph")
#install.packages("randomForest")
#install.packages("RcppEigen")
#install.packages("ranger")
#install.packages("wsrf")
#install.packages("RSNNS")

# Loading all needed libraries
library(kernlab)
library(gam)
library(kknn)
library(igraph)
library(randomForest)
library(RcppEigen)
library(ranger)
library(wsrf)
library(RSNNS)
library(dplyr)
library(tidyverse)
library(caret)
library(kableExtra)
library(tidyr)
library(stringr)
library(forcats)
library(ggplot2)
library(splines)
library(foreach)
library(mgcv)
library(nlme)
library(data.table)

```

## Loading the Heart dieseas(HD) Dataset
```{r}
HD <- read_csv("C:/Users/yashp/Downloads/archive/Hearts.csv",show_col_types = FALSE)

# changing the column name for making it more descriptive.

names(HD) <- c("age", "sex", "chest_pain_type", "resting_blood_pressure",
                   "cholesterol", "fasting_blood_sugar", "rest_ecg",
                   "max_heart_rate_achieved", "exercise_induced_angina",
                   "st_depression", "st_slope", "num_major_vessels",
                   "thallium_stress_test", "disease")

# converts disease as  "0" or "1" for using it with confusionMatrix()

HD <- mutate_at(HD, vars(disease), as.factor)


```
## Spliting HD dataset in HDX and validation sets
```{r}
set.seed(1) 
# Validation set will be 20% of HD data because it is a little dataset

test_index <- createDataPartition(y = HD$disease,
                                  times = 1, p = 0.2, list = FALSE) 
HDX <- HD[-test_index,]
validation <- HD[test_index,] # we will use it only to do final test

```

## Spliting HDX dataset in train_set and test_set
```{r}
set.seed(1)

test_index <- createDataPartition(y = HDX$disease,
                                  times = 1, p = 0.2, 
                                  list = FALSE)  # test_set 20%
train_set <- HDX[-test_index,]
test_set <- HDX[test_index,]


#  We will use it to train ours models

```

## List of models and usinf trainControl function for tuning parameter
```{r}
# model list
models <- c("glm", "lda", "naive_bayes", "svmLinear",
            "gamLoess", "knn", "kknn","gam",
            "rf", "ranger", "wsrf", "mlp")

# using trainControl function for control tuning parameters of models

control <- trainControl(method = "cv",   # cross validation
                        number = 10,     # 10 k-folds or number 
                        # of resampling iterations
                        )

```

## Initializing varialble and using loop
```{r}
train_data <- train_set      
test_data <-  test_set        
correct_value <- test_set$disease # Correct outcome from test_set 

# loop to use train and test set first, then HDX, then validation

for(i in 1:2) {       
  fits <- lapply(models, function(model){ 
    #    print(model)  # it´s used to debug code
    set.seed(1)
    train(disease ~ .,
          method = model,
          preProcess=c("center", "scale"),   # to normalize the data
          data = train_data,
          trControl = control)
  }) 
  
names(fits) <- models
  
  # to be sure that the actual value of the output do not have influence on the prediction
  
vali2 <- test_data %>% select(-disease) 
  
pred <- sapply(fits, function(object) # predicting outcome
predict(object, newdata = vali2))
  
  # avg predicted values if equals to true values
  
  if (i == 1) acc <- colMeans(pred == correct_value)
  
  train_data <- HDX               # last value for data parameter
  test_data <-  validation        # last we´ll use HDX and validation
  correct_value <- validation$disease  # true outcome from validation set
  
}

```

### Results of different models on 2 different datasets: first train/test_set, and edx/validation
```{r}

acc    # all accuracy values with Train and Test set

acc2 <- colMeans(pred == correct_value) # avg predicted values

acc2   # all accuracy values with HDX and Validation set

results <- acc2 - acc # accuracy diff by model


results


```
# Computing balance accuracy, sensitivity, specificity,prevalence with confusionMatrix
```{r}


confmat_val_HD<- confusionMatrix(as.factor(pred[,11]),
                                       validation$disease, positive = "1")
confmat_val_HD


```
## Using KNN Algorithm As it is overall the best Algorithm/model/method
```{r}


# to be sure that the actual value of the output has not influence on the prediction

vali02 <- validation %>% select(-disease)

# trainControl function for control iteration model
# we test differents parameters and choose that ones that improve accuracy

control02 <- trainControl(method = "cv",   # cross validation
                        number = 30)   # optimum k-folds or number 30
# of resampling iterations

# training KNN model

set.seed(1)
knn_model <- train(disease ~., data = HDX,
                      method = "knn",  # KNN model
                      preProcess=c("center", "scale"),   # to normalize the data
                      trControl = control02)

# predicting outcome

prediction_knn <- predict(knn_model, newdata = vali02)

# Check results with confusionMatrix() function and validation set

confmat_knn<- confusionMatrix(prediction_knn,
                                   validation$disease, positive = "1")
confmat_knn


```

